Adaptive Video Streaming with PID-Based Quality Control and Optimized Bitstream Extraction

### 2015-05-06 tmm.tex
refined abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
To cope with the challenge brought by bandwidth fluctuation and provide the user with best quality of service, this paper proposes an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology and integrates novel models and algorithms. First, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment according to actual bandwidth condition. By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm determines a suitable bitrate for transmission. Then, under the constraint of that bitrate, an efficient scheme is used to extract an optimal sub-stream from the whole SVC video bitstream. In this scheme, a linear error model enables accurate estimation of the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value for Rate-Distortion optimized bitstream extraction. Experimental results show that by combining the above algorithms, PSNR average can be increased from 40.29 to 40.62, and PSNR variance can be reduced from 0.66 to 0.28, i.e., both higher video quality and lower quality fluctuation are achieved. The proposed system is also implemented in online video website www.7dlive.com and proves to be practically effective.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
To cope with the challenge brought by bandwidth fluctuation and provide the user with video of both smooth and high quality, an adaptive video streaming framework is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC. First, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment according to actual bandwidth condition. By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm determines a suitable bitrate for transmission. Then, under the constraint of that bitrate, an efficient scheme is used to extract an optimal sub-stream from the whole SVC video bitstream. In this scheme, a linear error model which exploits the linear feature of pixel value errors is used to accurately estimate the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction. Experimental results show that, comparing with the baseline software, the proposed framework integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.66 to 0.28, and at the same time deliver higher video quality, with an average PSNR gain of 0.33dB. The framework is deployed at online video website www.7dlive.com and proves to be practically effective.
\end{abstract}
